---
title: "Hackathon"
author: "Tupi Guaranis"
date: "07/12/2021"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: yeti
---

```{r setup, include=FALSE}


#------------------------------------------------------------------------
require(pacman)

pacman::p_load(leaflet, leaflet.extras, leaflet.providers, 
               leafem, htmlwidgets, dplyr, htmltools, rgdal, 
               leafem, mapview, tmap, ggplot2)
#------------------------------------------------------------------------

paises <- readOGR("countries.geojson")

# dados:

# logo:
m <- "https://images.vexels.com/media/users/3/143561/isolated/preview/afa3aa927b63061e3b0222b7dab9cdbf-ubicaci--n-n--utica-norte-flecha-vintage-by-vexels.png"

AA <- leaflet(paises) %>%
  addControl(html = "<p><strong><em>Título</em></strong></p>", position ="topright")%>%
  
  addLogo(m,url = "https://images.vexels.com/media/users/3/143561/isolated/preview/afa3aa927b63061e3b0222b7dab9cdbf-ubicaci--n-n--utica-norte-flecha-vintage-by-vexels.png",
          position = "topleft", offset.x = 50, offset.y = 10, width = 100, height = 100) %>%
  
  addProviderTiles(providers$OpenStreetMap) %>%
  
  setView(lng = 90, lat = 10, zoom = 1) %>%
   
  addLayersControl(baseGroups = c("OSM","Satellite"), 
                   overlayGroups = c("Study Area"),
                   position = "topright", options = layersControlOptions(collapsed = TRUE)) %>%
  
  addProviderTiles(providers$OpenStreetMap, group = "OSM") %>%
  
  addProviderTiles(providers$Esri.WorldImagery, group = "Satellite") %>%
  
  addMiniMap(tiles = providers$Esri.WorldImagery, toggleDisplay = TRUE) 


### outros gráficos

graph2 <- mtcars %>%
 ggplot() +
 aes(x = mpg, y = drat, colour = as.factor(gear)) +
 geom_point(shape = "circle", size = 1.5) +
 labs(x = "Miles per Galoon", colour = "gear")+
 theme_minimal()

graph3 <- CO2 %>% 
  ggplot() +
  aes(x = conc, y = uptake, colour = as.factor(Treatment)) +
  geom_point(shape = "circle", size = 1.5) +
  labs(x = "Concentration", colour = "treatment")+
  theme_minimal()


```




Título geral
===================================== 

Column {data-width=600}
-----------------------------------------------------------------------

### Gráfico 1
```{r map}
AA
```

Column {data-width=400}
-----------------------------------------------------------------------

### Gráfico 2

```{r map1}
graph2                                                  
```

### Gráfico 3

```{r map2}
graph3
```


Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 

### Hackathon report

At this report there are the main results from the Hackathon challenge with the objective of become 
easier to spread our analysis throughout community
about...
 
\  

Therefore we used the following databases:

\  

* x [link]()

* y [link]()

\   

The main variables selected to generate these analysis were:

\  

* w

* z

\   

You can see all the data used during this challenge through this [link]() and the repository with the code [here]()

\  

``` authors: Eloabe; Gabriel; Gustavo; Pedro; Hugo ```
